---
title: "Performance Measures"
author: "Felix Adamaszek"
---

# Weiterführung aus challenge 4 - Was wird noch gebraucht?




# Leaderboard visualization (for Challenge 5)

```{r}
data_transformed_tbl <- automl_models_h2o@leaderboard %>%
  as_tibble() %>%
  select(-c(aucpr, mean_per_class_error, rmse, mse)) %>% 
  mutate(model_type = str_extract(model_id, "[^_]+")) %>%
  slice(1:15) %>% 
  rownames_to_column(var = "rowname") %>%
  # Visually this step will not change anything
  # It reorders the factors under the hood
  mutate(
    model_id   = as_factor(model_id) %>% reorder(auc),
    model_type = as.factor(model_type)
  ) %>% 
  pivot_longer(cols = -c(model_id, model_type, rowname), 
               names_to = "key", 
               values_to = "value", 
               names_transform = list(key = forcats::fct_inorder)
  ) %>% 
  mutate(model_id = paste0(rowname, ". ", model_id) %>% as_factor() %>% fct_rev())

data_transformed_tbl %>%
  ggplot(aes(value, model_id, color = model_type)) +
  geom_point(size = 3) +
  geom_label(aes(label = round(value, 2), hjust = "inward")) +
  
  # Facet to break out logloss and auc
  facet_wrap(~ key, scales = "free_x") +
  labs(title = "Leaderboard Metrics",
       subtitle = paste0("Ordered by: ", "auc"),
       y = "Model Postion, Model ID", x = "") + 
  theme(legend.position = "bottom")

```

# Cowplot (Challenge 5)
```{r}
theme_new <- theme(
  legend.position  = "bottom",
  legend.key       = element_blank(),
  panel.background = element_rect(fill   = "transparent"),
  panel.border     = element_rect(color = "black", fill = NA, size = 0.5),
  panel.grid.major = element_line(color = "grey", size = 0.333)
)

h2o.init()
newdata <- test_data
order_by <- "auc"
max_models <- 4
size <- 1

plot_h2o_performance <- function(h2o_leaderboard, newdata, order_by = c("auc", "logloss"),
                                 max_models = 3, size = 1.5) {
  
  # Inputs
  
  leaderboard_tbl <- h2o_leaderboard %>%
    as_tibble() %>%
    slice(1:max_models)
  
  newdata_tbl <- newdata %>%
    as_tibble()
  
  # Selecting the first, if nothing is provided
  order_by      <- tolower(order_by[[1]]) 
  
  # Convert string stored in a variable to column name (symbol)
  order_by_expr <- rlang::sym(order_by)
  
  # Turn of the progress bars ( opposite h2o.show_progress())
  h2o.no_progress()
  
  # 1. Model metrics
  
  get_model_performance_metrics <- function(model_id, test_data) {
    
    model_h2o <- h2o.getModel(model_id)
    perf_h2o  <- h2o.performance(model_h2o, newdata = as.h2o(test_data))
    
    perf_h2o %>%
      h2o.metric() %>%
      as.tibble() %>%
      select(threshold, tpr, fpr, precision, recall)
    
  }
  
  model_metrics_tbl <- leaderboard_tbl %>%
    mutate(metrics = map(model_id, get_model_performance_metrics, newdata_tbl)) %>%
    unnest(cols = metrics) %>%
    mutate(
      model_id = as_factor(model_id) %>% 
        # programmatically reorder factors depending on order_by
        fct_reorder(!! order_by_expr, 
                    .desc = ifelse(order_by == "auc", TRUE, FALSE)),
      auc      = auc %>% 
        round(3) %>% 
        as.character() %>% 
        as_factor() %>% 
        fct_reorder(as.numeric(model_id)),
      logloss  = logloss %>% 
        round(4) %>% 
        as.character() %>% 
        as_factor() %>% 
        fct_reorder(as.numeric(model_id))
    )
  
  
  # 1A. ROC Plot
  
  p1 <- model_metrics_tbl %>%
    ggplot(aes(fpr, tpr, color = model_id, linetype = !! order_by_expr)) +
    geom_line(size = size) +
    theme_new +
    labs(title = "ROC", x = "FPR", y = "TPR") +
    theme(legend.direction = "vertical") 
  
  
  # 1B. Precision vs Recall
  
  p2 <- model_metrics_tbl %>%
    ggplot(aes(recall, precision, color = model_id, linetype = !! order_by_expr)) +
    geom_line(size = size) +
    theme_new +
    labs(title = "Precision Vs Recall", x = "Recall", y = "Precision") +
    theme(legend.position = "none") 
  
  
  # 2. Gain / Lift
  
  get_gain_lift <- function(model_id, test_data) {
    
    model_h2o <- h2o.getModel(model_id)
    perf_h2o  <- h2o.performance(model_h2o, newdata = as.h2o(test_data)) 
    
    perf_h2o %>%
      h2o.gainsLift() %>%
      as.tibble() %>%
      select(group, cumulative_data_fraction, cumulative_capture_rate, cumulative_lift)
    
  }
  
  gain_lift_tbl <- leaderboard_tbl %>%
    mutate(metrics = map(model_id, get_gain_lift, newdata_tbl)) %>%
    unnest(cols = metrics) %>%
    mutate(
      model_id = as_factor(model_id) %>% 
        fct_reorder(!! order_by_expr, 
                    .desc = ifelse(order_by == "auc", TRUE, FALSE)),
      auc  = auc %>% 
        round(3) %>% 
        as.character() %>% 
        as_factor() %>% 
        fct_reorder(as.numeric(model_id)),
      logloss = logloss %>% 
        round(4) %>% 
        as.character() %>% 
        as_factor() %>% 
        fct_reorder(as.numeric(model_id))
    ) %>%
    rename(
      gain = cumulative_capture_rate,
      lift = cumulative_lift
    ) 
  
  # 2A. Gain Plot
  
  p3 <- gain_lift_tbl %>%
    ggplot(aes(cumulative_data_fraction, gain, 
               color = model_id, linetype = !! order_by_expr)) +
    geom_line(size = size,) +
    geom_segment(x = 0, y = 0, xend = 1, yend = 1, 
                 color = "red", size = size, linetype = "dotted") +
    theme_new +
    expand_limits(x = c(0, 1), y = c(0, 1)) +
    labs(title = "Gain",
         x = "Cumulative Data Fraction", y = "Gain") +
    theme(legend.position = "none")
  
  # 2B. Lift Plot
  
  p4 <- gain_lift_tbl %>%
    ggplot(aes(cumulative_data_fraction, lift, 
               color = model_id, linetype = !! order_by_expr)) +
    geom_line(size = size) +
    geom_segment(x = 0, y = 1, xend = 1, yend = 1, 
                 color = "red", size = size, linetype = "dotted") +
    theme_new +
    expand_limits(x = c(0, 1), y = c(0, 1)) +
    labs(title = "Lift",
         x = "Cumulative Data Fraction", y = "Lift") +
    theme(legend.position = "none") 
  
  
  # Combine using cowplot
  
  # cowplot::get_legend extracts a legend from a ggplot object
  p_legend <- get_legend(p1)
  # Remove legend from p1
  p1 <- p1 + theme(legend.position = "none")
  
  # cowplot::plt_grid() combines multiple ggplots into a single cowplot object
  p <- cowplot::plot_grid(p1, p2, p3, p4, ncol = 2)
  
  # cowplot::ggdraw() sets up a drawing layer
  p_title <- ggdraw() + 
    
    # cowplot::draw_label() draws text on a ggdraw layer / ggplot object
    draw_label("H2O Model Metrics", size = 18, fontface = "bold", 
               color = "#2C3E50")
  
  p_subtitle <- ggdraw() + 
    draw_label(glue("Ordered by {toupper(order_by)}"), size = 10,  
               color = "#2C3E50")
  
  # Combine everything
  ret <- plot_grid(p_title, p_subtitle, p, p_legend, 
                   
                   # Adjust the relative spacing, so that the legends always fits
                   ncol = 1, rel_heights = c(0.05, 0.05, 1, 0.05 * max_models))
  
  h2o.show_progress()
  
  return(ret)
  
}

automl_models_h2o@leaderboard %>%
  plot_h2o_performance(newdata = test_data, order_by = "logloss", 
                       size = 0.5, max_models = 4)