---
title: "Automated Machine Learning with H20 (I)"
author: "Felix Adamaszek"
---

# Loading required libraries

```{r}
    library(tidyverse)
    library(GGally)

    employee_attrition_tbl <- read_csv("/Users/felixadamaszek/Documents/GitHub/ss23-bdml-FelixAdams1827/ss23-bdml-FelixAdams1827/content/01_journal/H2O Data/datasets-1067-1925-WA_Fn-UseC_-HR-Employee-Attrition.csv")
  
```

# Interaction between Monthly Income and Attrition?

```{r}

# a. Those that are leaving the company have a higher Monthly Income?
# b. That those are staying have a lower Monthly Income
# c. Those that are leaving have a lower Monthly Income
# d. It's difficult to deduce anything based on the visualization

employee_attrition_tbl %>% 
  select(Attrition, MonthlyIncome) %>% 
  ggpairs(aes(color = Attrition), lower = "blank", legend = 1,
            diag  = list(continuous = wrap("densityDiag", alpha = 0.5))) +
    theme(legend.position = "bottom")
```

Answer c. should be correct

# Interaction between Percent Salary Hike and Attrition?

```{r}

# a. Those that are leaving the company have a higher Percent Salary Hike
# b. Those that are staying have a lower Percent Salary Hike
# c. Those that are leaving have lower Percent Salary Hike
# d. It's difficult to deduce anything based on the visualization

employee_attrition_tbl %>% 
  select(Attrition, PercentSalaryHike) %>% 
  ggpairs(aes(color = Attrition), lower = "blank", legend = 1,
            diag  = list(continuous = wrap("densityDiag", alpha = 0.5))) +
    theme(legend.position = "bottom")
```

Answer d..

# Interaction between Stock Option Level and Attrition?

```{r}

# a. Those that are leaving the company have a higher stock option level
# b. Those that are staying have a higher stock option level
# c. It's difficult to deduce anything based on the visualization

employee_attrition_tbl %>% 
  select(Attrition, StockOptionLevel) %>% 
  ggpairs(aes(color = Attrition), lower = "blank", legend = 1,
            diag  = list(continuous = wrap("densityDiag", alpha = 0.5))) +
    theme(legend.position = "bottom")
```

Answer c..

# Interaction between Environment Satisfaction and Attrition?

```{r}
# a. A higher proportion of those leaving have a low environment satisfaction level
# b. A higher proportion of those leaving have a high environment satisfaction level
# c. It's difficult to deduce anything based on the visualization

employee_attrition_tbl %>% 
  select(Attrition, EnvironmentSatisfaction) %>% 
  ggpairs(aes(color = Attrition), lower = "blank", legend = 1,
            diag  = list(continuous = wrap("densityDiag", alpha = 0.5))) +
    theme(legend.position = "bottom")
```

Answer a..

# Interaction between Work Life Balance and Attrition?

```{r}
# a. Those that are leaving have higher density of 2's and 3's
# b. Those that are staying have a higher density of 2's and 3's
# c. Those that are staying have a lower density of 2's and 3's
# d. It's difficult to deduce anything based on the visualization

employee_attrition_tbl %>% 
  select(Attrition, WorkLifeBalance) %>% 
  ggpairs(aes(color = Attrition), lower = "blank", legend = 1,
            diag  = list(continuous = wrap("densityDiag", alpha = 0.5))) +
    theme(legend.position = "bottom")
```

Answer b..

# Interaction between Job Involvement and Attrition?

```{r}
# a. Those that are leaving have a lower density of 3's and 4's
# b. Those that are leaving have a lower density of 1's and 2's
# c. Those that are staying have a lower density of 2's and 3's
# d. It's difficult to deduce anything based on the visualization

employee_attrition_tbl %>% 
  select(Attrition, JobInvolvement) %>% 
  ggpairs(aes(color = Attrition), lower = "blank", legend = 1,
            diag  = list(continuous = wrap("densityDiag", alpha = 0.5))) +
    theme(legend.position = "bottom")
```

Answer a..

# Interaction between Over Time and Attrition?

```{r}
# a. The proportion of those leaving that are working Over Time are high compared to those that are not leaving
# b. The proportion of those staying that are working Over Time are high compared to those that are not staying

employee_attrition_tbl %>% 
  select(Attrition, OverTime) %>% 
  ggpairs(aes(color = Attrition), lower = "blank", legend = 1,
            diag  = list(continuous = wrap("densityDiag", alpha = 0.5))) +
    theme(legend.position = "bottom")
```

Answer b..

# Interaction between Training Times Last Year and Attrition?

```{r}
# a. People that leave tend to have more annual trainings
# b. People that leave tend to have less annual trainings
# c. It's difficult to deduce anything based on the visualization

employee_attrition_tbl %>% 
  select(Attrition, TrainingTimesLastYear) %>% 
  ggpairs(aes(color = Attrition), lower = "blank", legend = 1,
            diag  = list(continuous = wrap("densityDiag", alpha = 0.5))) +
    theme(legend.position = "bottom")
```

Answer c..


# Interaction between Years At Company and Attrition?

```{r}
# a. People that leave tend to have more working years at the company
# b. People that leave tend to have less working years at the company
# c. It's difficult to deduce anything based on the visualization

employee_attrition_tbl %>% 
  select(Attrition, YearsAtCompany) %>% 
  ggpairs(aes(color = Attrition), lower = "blank", legend = 1,
            diag  = list(continuous = wrap("densityDiag", alpha = 0.5))) +
    theme(legend.position = "bottom")
```

Answer b..

# Interaction between Years Since Last Promotion and Attrition?

```{r}
# a. Those that are leaving have more years since last promotion than those that are staying
# b. Those that are leaving have fewer years since last promotion than those that are staying
# c. It's difficult to deduce anything based on the visualization

employee_attrition_tbl %>% 
  select(Attrition, YearsSinceLastPromotion) %>% 
  ggpairs(aes(color = Attrition), lower = "blank", legend = 1,
            diag  = list(continuous = wrap("densityDiag", alpha = 0.5))) +
    theme(legend.position = "bottom")
```

Answer c..